---
title: "Intro to Brewing"
output: html_document
---

**`brew`** is an R package that provides a templating system for text reporting. ([vignette](https://cran.r-project.org/web/packages/brew/brew.pdf))

Note: when you are really brewing, it probably makes more sense to do this from a `.R` file, not `.Rmd`.


(also note: fyi the R `brew` package is different from 'homebrewing', which is something ohi-webapp creation also uses from the command line to run imageMagick to resize images.)


## Example README:

[chn's reports/README.md](https://github.com/OHI-Science/chn/blob/draft/province2015/reports/README.md)

This was made from a template, let's take a look: 

- by convension we put a `.brew` before the `.md`

[template reports/README_reports.brew.md](https://github.com/OHI-Science/ohi-webapps/blob/master/README_reports.brew.md)


OK, so how do we set those variables: 

```{r}

# libraries
library(knitr)
library(brew) # install.packages('brew')

# directories
dir_webapps  = '~/github/ohi-webapps'
dir_tutorial = '~/github/ohimanual/tutorials/brew_intro'

# read in data
sc_studies = read.csv(file.path(dir_webapps, 'custom/sc_studies_custom.csv'))
kable(sc_studies)

# select some variables
keys = sc_studies$sc_key

for (key in keys) { # key = 'chn'
  
  i             = which(sc_studies$sc_key==key)
  sc            = sc_studies[i,]
  
  study_area = sc$sc_name; study_area
  scenario   = sc$default_scenario; scenario
  year       = sc$year; year
  html_name  = paste0(study_area, year); html_name

}

```


## And brew!
just one line of code, really: 

```{r}
for (key in keys) { # key = 'bhi'
  
  i             = which(sc_studies$sc_key==key)
  sc            = sc_studies[i,]
  
  study_area = as.character(sc$sc_name); study_area
  scenario   = sc$default_scenario; scenario
  year       = sc$year; year
  html_name  = paste0(study_area, year); html_name
  
  
  brew(file.path(dir_webapps,  'README_reports.brew.md'), 
       file.path(dir_tutorial, paste0('README_',study_area, '.md')))
  
}


```

